---
title: "Quiz 3"
output: html_document
---
```{r}
library(knitr)
```

Question 1

_When you breathe, I want to be the air for you. I'll be there for you, I'd live and I'd_
http://www.bonjovi.com/music/39333067588/this-left-feels-right/lyrics/40537307034/ill-be-there-for-you#.VoolVvkrIpY

*give {inital estimate}
*die [X] - 
*eat
*sleep

```{r}

wordOptions <- c("give","die","eat","sleep")
uni.words <- freq.uni%>%filter(word %in% wordOptions)%>%arrange(desc(freq))
bi.words <- freq.bi%>%filter(word %in% paste("id",wordOptions))%>%arrange(desc(freq))
tri.words <- freq.tri%>%filter(word %in% paste("and id",wordOptions))%>%arrange(desc(freq))
quad.words <- freq.quad%>%filter(word %in% paste("live and id",wordOptions))%>%arrange(desc(freq))

                

```


Guy at my table's wife got up to go to the bathroom and I asked about dessert and he started telling me about his

* spiritual (2)
* horticultural
financial  (1)
marital  {Seems like this may be it}

```{r, echo=FALSE}
a2 <- freq.quad%>%filter(grepl("^me about his.*",words))

wordOptions <- c("spiritual","horticultural","financial","marital")
uni.words <- freq.uni%>%filter(word %in% wordOptions)%>%arrange(desc(freq))
bi.words <- freq.bi%>%filter(word %in% paste("his",wordOptions))%>%arrange(desc(freq))
tri.words <- freq.tri%>%filter(word %in% paste("about his",wordOptions))%>%arrange(desc(freq))
quad.words <- freq.quad%>%filter(word %in% paste("me about his",wordOptions))%>%arrange(desc(freq))
quad.words.4 <- freq.quad%>%filter(grepl("wife .*marital",word))%>%arrange(desc(freq))


```

I'd give anything to see arctic monkeys this
month
morning
decade
weekend

Here is where the algorithim computes based on first word and last 2 words using the quadgram.   
When doing this, the "weekend" wins
When using a bigram - "morning" wins


```{r, echo=FALSE}
 
wordOptions <- c("month",
"morning",
"decade",
"weekend")
uni.words <- freq.uni%>%filter(word %in% wordOptions)%>%arrange(desc(freq))
bi.words <- freq.bi%>%filter(word %in% paste("this",wordOptions))%>%arrange(desc(freq))
tri.words <- freq.tri%>%filter(word %in% paste("monkeys this",wordOptions))%>%arrange(desc(freq))
tri.words.1 <- freq.tri%>%filter(grepl(".*this month$",word))%>%arrange(desc(freq))
tri.words.2 <- freq.tri%>%filter(grepl(".*this morning$",word))%>%arrange(desc(freq))
tri.words.3 <- freq.tri%>%filter(grepl(".*this decade$",word))%>%arrange(desc(freq))
tri.words.4 <- freq.tri%>%filter(grepl(".*this weekend$",word))%>%arrange(desc(freq))
quad.words.1 <- freq.quad%>%filter(grepl(".*this month$",word))%>%arrange(desc(freq))
quad.words.2 <- freq.quad%>%filter(grepl("^see .*this morning$",word))%>%arrange(desc(freq))
quad.words.3 <- freq.quad%>%filter(grepl("^see .*this decade$",word))%>%arrange(desc(freq))
quad.words.4 <- freq.quad%>%filter(grepl("^see .*this weekend$",word))%>%arrange(desc(freq))

```

Talking to your mom has the same effect as a hug and helps reduce your
hunger
stress
sleepiness
happiness

```{r}
wordOptions <- c("hunger",
"stress",
"sleepiness",
"happiness")
uni.words <- freq.uni%>%filter(word %in% wordOptions)%>%arrange(desc(freq))
bi.words <- freq.bi%>%filter(word %in% paste("your",wordOptions))%>%arrange(desc(freq))
tri.words <- freq.tri%>%filter(word %in% paste("reduce your",wordOptions))%>%arrange(desc(freq))
tri.words.1 <- freq.tri%>%filter(grepl(".*this month$",word))%>%arrange(desc(freq))
tri.words.2 <- freq.tri%>%filter(grepl(".*this morning$",word))%>%arrange(desc(freq))
tri.words.3 <- freq.tri%>%filter(grepl(".*this decade$",word))%>%arrange(desc(freq))
tri.words.4 <- freq.tri%>%filter(grepl(".*this weekend$",word))%>%arrange(desc(freq))

quad.words <- freq.quad%>%filter(grepl("hug .*reduce your.*",word))%>%arrange(desc(freq))
quad.words.1 <- freq.quad%>%filter(grepl(".*this month$",word))%>%arrange(desc(freq))

quad.words.1 <- freq.quad%>%filter(grepl(".*this month$",word))%>%arrange(desc(freq))
quad.words.2 <- freq.quad%>%filter(grepl("^see .*this morning$",word))%>%arrange(desc(freq))
quad.words.3 <- freq.quad%>%filter(grepl("^see .*this decade$",word))%>%arrange(desc(freq))
quad.words.4 <- freq.quad%>%filter(grepl("^see .*this weekend$",word))%>%arrange(desc(freq))


````

When you were in Holland you were like 1 inch away from me but you hadn't time to take a
look
minute
walk
picture


```{r}
wordOptions <- c("look",
"minute",
"walk",
"picture")
uni.words <- freq.uni%>%filter(word %in% wordOptions)%>%arrange(desc(freq))
bi.words <- freq.bi%>%filter(word %in% paste("a",wordOptions))%>%arrange(desc(freq))
tri.words <- freq.tri%>%filter(word %in% paste("take a",wordOptions))%>%arrange(desc(freq))
tri.words.1 <- freq.tri%>%filter(grepl(".*this month$",word))%>%arrange(desc(freq))
tri.words.2 <- freq.tri%>%filter(grepl(".*this morning$",word))%>%arrange(desc(freq))
tri.words.3 <- freq.tri%>%filter(grepl(".*this decade$",word))%>%arrange(desc(freq))
tri.words.4 <- freq.tri%>%filter(grepl(".*this weekend$",word))%>%arrange(desc(freq))

quad.words <- freq.tri%>%filter(word %in% paste("to take a",wordOptions))%>%arrange(desc(freq))
quad.words.1 <- freq.quad%>%filter(grepl(".*this month$",word))%>%arrange(desc(freq))

quad.words.1 <- freq.quad%>%filter(grepl(".*this month$",word))%>%arrange(desc(freq))
quad.words.2 <- freq.quad%>%filter(grepl("^see .*this morning$",word))%>%arrange(desc(freq))
quad.words.3 <- freq.quad%>%filter(grepl("^see .*this decade$",word))%>%arrange(desc(freq))
quad.words.4 <- freq.quad%>%filter(grepl("^see .*this weekend$",word))%>%arrange(desc(freq))


```



I'd just like all of these questions answered, a presentation of evidence, and a jury to settle the
matter
account
case
incident
```{r}
wordOptions <- c("matter",
"account",
"case",
"incident")
uni.words <- freq.uni%>%filter(word %in% wordOptions)%>%arrange(desc(freq))
bi.words <- freq.bi%>%filter(word %in% paste("the",wordOptions))%>%arrange(desc(freq))
tri.words <- freq.tri%>%filter(word %in% paste("settle the",wordOptions))%>%arrange(desc(freq))
quad.words <- freq.tri%>%filter(word %in% paste("to settle the",wordOptions))%>%arrange(desc(freq)) 
```

I can't deal with unsymetrical things. I can't even hold an uneven number of bags of groceries in each
toe
hand
finger
arm


```{r}
wordOptions <- c("toe",
"hand",
"finger",
"arm")
uni.words <- freq.uni%>%filter(word %in% wordOptions)%>%arrange(desc(freq))
bi.words <- freq.bi%>%filter(word %in% paste("each",wordOptions))%>%arrange(desc(freq))
tri.words <- freq.tri%>%filter(word %in% paste("in each",wordOptions))%>%arrange(desc(freq))
quad.words <- freq.tri%>%filter(word %in% paste("groceries in each",wordOptions))%>%arrange(desc(freq)) 
```

#Question 8
Every inch of you is perfect from the bottom to the
center
top
middle
side

```{r}
wordOptions <- c("center",
"top",
"middle",
"side")
uni.words <- freq.uni%>%filter(word %in% wordOptions)%>%arrange(desc(freq))
bi.words <- freq.bi%>%filter(word %in% paste("the",wordOptions))%>%arrange(desc(freq))
tri.words <- freq.tri%>%filter(word %in% paste("to the",wordOptions))%>%arrange(desc(freq))
quad.words <- freq.tri%>%filter(word %in% paste("bottom to the",wordOptions))%>%arrange(desc(freq)) 
```

Question 9
I’m thankful my childhood was filled with imagination and bruises from playing
weekly
daily
outside
inside

```{r}
wordOptions <- c("weekly",
"daily",
"outside",
"inside")
uni.words <- freq.uni%>%filter(word %in% wordOptions)%>%arrange(desc(freq))
bi.words <- freq.bi%>%filter(word %in% paste("playing",wordOptions))%>%arrange(desc(freq))
tri.words <- freq.tri%>%filter(word %in% paste("from playing",wordOptions))%>%arrange(desc(freq))
quad.words <- freq.tri%>%filter(word %in% paste("bruises from playing",wordOptions))%>%arrange(desc(freq)) 
```

Question 10
I like how the same people are in almost all of Adam Sandler's
pictures
movies
novels
stories


```{r}
wordOptions <- c("novels",
"movies",
"stories",
"pictures")
uni.words <- freq.uni%>%filter(word %in% wordOptions)%>%arrange(desc(freq))
bi.words <- freq.bi%>%filter(word %in% paste("sandlers",wordOptions))%>%arrange(desc(freq))
tri.words <- freq.tri%>%filter(word %in% paste("adam sandler",wordOptions))%>%arrange(desc(freq))
quad.words <- freq.tri%>%filter(word %in% paste("of adam sandlers",wordOptions))%>%arrange(desc(freq)) 
```